---
fontsize: 12pt
geometry: "left=1.5cm,right=1.5cm, top=2cm, bottom=2.75cm"
mainfont: Calibri Light
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: FALSE
    latex_engine: xelatex
  html_document:
    df_print: 
classoption: landscape
urlcolor: blue
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

options(knitr.table.format = 'latex', knitr.kable.NA = '')

#load chunks from r script
# knitr::read_chunk("AnnualReportChunks.R")


```



**Pre-season DB:** `r pre.season.db.name` , **Pre-season run name:** `r run.name`  \newline


 **Table 1: Summary of the `r run.year` pre-season return of natural spawning Coho Management Units.**
                    Total pre-season exploitation rate (ER) represents the sum of US and Canadian exploitation rates on each
                    Management Unit (MU). Status (i.e., "L"ow, "M"oderate, "A"bundant) is based on cohort abundance.
                    Pre-season status is based on agency forecasts of MU cohort abundance.
                    The ER Cap on the Interior Fraser MU is 20% due to its Low MU status.
                    ER Caps are not available for other Canadian MUs. ER Caps on each of the Inside US MUs
                    (Skagit, Stillaguamish, Snohomish, Hood Canal, and US Strait JDF) are based on MU status,
                    which is determined by cohort abundance. ER Caps on each of the Outside US MUs
                    (Quillayute Fall, Queets, Hoh, Grays Harbor) are based on cohort abundance and the escapement goals
                    for each MU. Outside US MUs are managed for an escapement range; the floor of the escapement range
                    is used for MU status determination. Pre-season modelled ERs are the result of US and Canadian fishery
                    planning processes. Cohort abundance is the ocean age-3 abundance and represents escapement plus fishery mortality,
                    but not natural mortality.




```{r firsttable, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

t2 <- CreateTable1(pre.season.data = pre.season.data, post.season.data = pre.season.data, run.year = run.year) %>%
  select(management.unit, us.pre.model, cdn.pre.model)

t1 <- CreateTable2(pre.season.data = pre.season.data, post.season.data = pre.season.data, run.year = run.year) %>%
  select(-post.cap, -post.estd, -post.ocean.age, -post.status ,-post.estd, -post.escapement) %>%
  mutate_if(colnames(.) %in% c("pre.cap", "pre.model",  "pre.escapement", "pre.ocean.age"), ~as.double(as.character(.))) %>%
  left_join(t2, "management.unit") %>%
  mutate_if(colnames(.) %in% c("pre.cap", "pre.model", "us.pre.model", "cdn.pre.model"),  ~percent(.,accuracy = 0.1)) %>%
  select(1:4, "us.pre.model", "cdn.pre.model", everything())



table1form <- kable(t1, format = "latex", digits = c(0), format.args = list(big.mark =","), escape = T,
                    col.names = c("Management unit", "Status", "ER Cap", "ER Model", "Southern US ER Model", "Cdn ER Model", "Escapement", "Recruitment (Ocean Age-3)"), label = "GUYUYUYUYUY",
                    booktabs = T, linesep = "") %>%
  kableExtra::column_spec(8:8, "2.5cm") %>%
  kable_styling(latex_options = "striped") %>%
  add_header_above(c(" ", "Pre-Season" = 7))

print(table1form)


```


\newpage 

**Table 3: Pre-season summary exploitation rates, escapements, and cohort abundances for naturally spawning Coho MUs in `r run.year`.**


```{r thirdtable, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

t3_per <- CreateTable3(pre.season.data) %>%
    filter(psc.fishery.name %notin% c("escapement", "cohort")) %>%
    mutate_if(is.numeric, ~percent(.,accuracy = 0.1, suffix = "\\%"))

t3_cnt <-CreateTable3(pre.season.data)%>%
  filter(psc.fishery.name %in% c("escapement", "cohort")) %>%
  mutate_if(is.numeric, ~comma(.))


t3_cnt_GS <- select(t3_cnt, c("psc.fishery.name", starts_with("Georgia")))

t3_cnt_GS[1,2:ncol(t3_cnt_GS)] <- paste0(t3_cnt_GS[1,2:ncol(t3_cnt_GS)], footnote_marker_symbol(3))
t3_cnt_GS[2,2:ncol(t3_cnt_GS)] <- paste0(t3_cnt_GS[2,2:ncol(t3_cnt_GS)], footnote_marker_symbol(2))

t3_cnt_oth <- select(t3_cnt, -starts_with("Georgia")) %>%
  mutate(`Lower Fraser` = if_else(psc.fishery.name == "escapement",
                                  paste0(`Lower Fraser`, footnote_marker_symbol(1)," "),
                                  paste0(`Lower Fraser`, footnote_marker_symbol(2))))

t3_cnt <- left_join(t3_cnt_GS, t3_cnt_oth, "psc.fishery.name")


t3 <- bind_rows(t3_per, t3_cnt) %>%
  mutate(psc.fishery.name = str_replace(psc.fishery.name, "&", "\\\\&")) %>%
  rename(`Fishery Name` = "psc.fishery.name") 


table3form <-  kable(t3, escape = F, booktabs= T, linesep = "", col.names = linebreak(c("Fishery name", "Georgia\nStrait", "Lower\nFraser","Interior\nFraser", "Skagit", "Stillaguamish", "Snohomish", "Hood Canal", "US Strait\nJDF", "Quillayute", "Hoh", "Queets", "Grays\nHarbor"))) %>%
  kable_styling(latex_options = c("scale_down")) %>%
  column_spec(1, bold = T) %>%
  row_spec(c(13, 23, 25), background = "#e3e7fc") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(seq(2, nrow(t3),2)), background = "#d6d6d6") %>%
  footnote(symbol = c("Modelled values of terminal run size occuring after lower Fraser in river fisheries", " Modelled values of terminal run size that are not directly estimated", "Modelled values that are not directly estimated"),threeparttable = T)


print(table3form)

```

