---
fontsize: 12pt
geometry: "left=1.5cm,right=1.5cm, top=2cm, bottom=2.75cm"
mainfont: Calibri Light
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: FALSE
    latex_engine: xelatex
  html_document:
    df_print: 
classoption: landscape
urlcolor: blue
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

options(knitr.table.format = 'latex', knitr.kable.NA = '')

#load chunks from r script
# knitr::read_chunk("AnnualReportChunks.R")


```

\thispagestyle{empty}

**Pre-season DB:** `r pre.season.db.name`, **Pre-season run name:** `r run.name`  \newline


 **Table 1: Summary of the `r run.year` pre-season return of natural spawning Coho Management Units.**
                    Total pre-season exploitation rate (ER) represents the sum of US and Canadian exploitation rates on each
                    Management Unit (MU). Pre-season status (i.e., "L"ow, "M"oderate, "A"bundant) is based on agency forecasts of MU cohort abundance.
                    For Canadian ER Caps on US MUs, the pre‐season ER Caps are the total allowable ER
under the PSC Coho agreement. For Canadian ER Caps on Canadian MUs, a 10% ER Cap for Interior Fraser Coho is allowable under the PSC Coho
agreement. Pre‐season ERs reflect combined US and Canadian pre‐season planning processes and do not include estimates of impacts in Canadian
freshwater fisheries. Pre‐season unused ERs are the difference between the ER Caps and modeled values.



```{r firsttable, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

big.bar.mort.txt <- format(round(big.bar.morts, 0), big.mark = ",")

t2 <- CreateTable1(pre.season.data = pre.season.data, post.season.data = pre.season.data, run.year = run.year) %>%
  select(-contains('post'), -"cap.method")
  # select(management.unit, us.pre.model, cdn.pre.model)

t2.ifc <-  filter(t2, management.unit == "Interior Fraser") 


t1.big.bar.row <-  CreateTable2(pre.season.data = pre.season.data, post.season.data = pre.season.data, run.year = run.year) %>%
  filter(management.unit == "Interior Fraser") %>%
  mutate(pre.escapement = as.character(big.bar.esc)) %>%
  mutate(pre.ocean.age = as.numeric(pre.ocean.age) - big.bar.morts) %>%
  mutate(pre.ocean.age = as.character(pre.ocean.age)) %>%
  mutate(pre.model = 1-(big.bar.esc/as.numeric(pre.ocean.age))) %>%
  mutate(pre.model = as.character(pre.model)) %>%
  mutate(management.unit = paste("Interior Fraser w/o Big Bar morts", footnote_marker_symbol(4, format = "latex"), sep=" ")) %>%
  select(-contains('post'))



t1.ifc <- CreateTable2(pre.season.data = pre.season.data, post.season.data = pre.season.data, run.year = run.year) %>%
  select(-contains('post')) %>%
  filter(management.unit == 'Interior Fraser')

ifc.oa <- t1.ifc$pre.ocean.age
ifc.esc <- t1.ifc$pre.escapement

ifc.bb.returns <- (as.numeric(ifc.oa) - big.bar.morts)

us.ifc.catch <- as.numeric(ifc.oa)*t2.ifc$us.pre.model
cdn.ifc.catch <- as.numeric(ifc.oa)*t2.ifc$cdn.pre.model
bb.us.er <- us.ifc.catch/ifc.bb.returns
bb.cdn.er <-  cdn.ifc.catch/ifc.bb.returns

t2.big.bar.row <- t2.ifc %>%
  mutate(us.pre.model = bb.us.er) %>%
  mutate(cdn.pre.model  = bb.cdn.er) %>%
  mutate(us.pre.unused = us.pre.cap - us.pre.model) %>%
  mutate(cdn.pre.unused = cdn.pre.cap - cdn.pre.model) %>%
  mutate(cdn.pre.cap = .10 + us.pre.unused) %>%
  mutate(management.unit = paste("Interior Fraser w/o Big Bar morts", footnote_marker_symbol(4, format = "latex"), sep=" ")) 

t2 <- add_row(t2, t2.big.bar.row)


t1 <- CreateTable2(pre.season.data = pre.season.data, post.season.data = pre.season.data, run.year = run.year) %>%
  select(-contains('post')) %>%
  tibble::add_row(t1.big.bar.row) %>%
  mutate_if(colnames(.) %in% c("pre.cap", "pre.model",  "pre.escapement", "pre.ocean.age"), ~as.double(as.character(.))) %>%
  mutate(pre.escapement = format(round(pre.escapement,0), big.mark = ",", trim = TRUE, na.encode = TRUE)) %>%
  mutate(pre.ocean.age = format(round(pre.ocean.age,0), big.mark = ",", trim = TRUE, na.encode = TRUE)) %>%
  # left_join(t2.big.bar.row, "management.unit", copy = TRUE) %>%
  left_join(t2, "management.unit") %>%
  mutate_if(colnames(.) %in% c("pre.cap", "pre.model", "us.pre.cap", "us.pre.model",  "us.pre.unused",  "cdn.pre.cap", "cdn.pre.model", "cdn.pre.unused"),  ~percent(.,accuracy = 0.1, suffix = "\\%")) %>%
  select(1:4, "us.pre.cap", "us.pre.model",  "us.pre.unused",  "cdn.pre.cap", "cdn.pre.model", "cdn.pre.unused", everything())%>%
  mutate(us.pre.cap = if_else(management.unit %in% c("Skagit", "Stillaguamish", "Snohomish", "Hood Canal", "US Strait JDF", "Quillayute", "Hoh", "Queets", "Grays Harbor"), paste(us.pre.cap, footnote_marker_symbol(3, "latex",), sep = " "), us.pre.cap ))%>%
  mutate(cdn.pre.cap = if_else(management.unit %in% c("Interior Fraser",  paste("Interior Fraser w/o Big Bar morts", footnote_marker_symbol(4, format = "latex"), sep=" ")), paste(cdn.pre.cap, footnote_marker_symbol(3, "latex"), sep = " "), cdn.pre.cap)) %>%
  mutate(pre.escapement = ifelse(pre.escapement == "NA", NA, pre.escapement)) %>%
  mutate(pre.ocean.age = ifelse(pre.ocean.age == "NA", NA, pre.ocean.age)) %>%
  slice(3, 1:2, 13, 4:12)


cdn_skag_unused <- t2$cdn.pre.unused[t2$management.unit == "Skagit"] %>%
  percent(., accuracy = 0.1)

us_skag_cap <- t2$us.pre.cap[t2$management.unit == "Skagit"] %>%
  percent(., accuracy = 0.1)

footnote3 <- "Including Southern Alaskan catch not included in this table (see table 2)."

footnote2 <- str_glue("Contains the base cap ER plus the unused portion of the intercepting party's ER. For example in the preseason, Skagit includes US share plus the unused {cdn_skag_unused} Canadian allocation, totalling {us_skag_cap} total US allocation.")

totalname <- paste("Total",footnote_marker_symbol(1, double_escape = T), sep=" ")
SusName <- paste("Southern US",footnote_marker_symbol(2, double_escape = T), sep=" ")


big.bar.footnote <- str_glue("Interior Fraser Coho ERs calculated using escapement without a conservative estimated 4,222 Big Bar mortalities (representing a complete blockage) are highlighted in yellow")


table1form <- kbl(t1, digits = 1,
                    col.names = c("Management unit", "Status", "ER Cap", "ER Model","US ER Cap", "US ER Model", "US Unused","Cdn Cap", "Cdn ER Model", "Cdn Unused",  "Escapement", "Recruitment (Ocean Age-3)"), escape = F,  linesep = "", booktabs = T, format = "latex") %>%
  # kableExtra::column_spec(8:8, "2.5cm") %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  add_header_above(c(" " = 2, setNames(2, totalname),   setNames(3, SusName), "Canadian" = 3), escape = FALSE)  %>%
  add_header_above(c(" ", "PreSeason" = 11)) %>%
  row_spec(c(seq(1, nrow(t1),2)), background = "gray!10") %>%
  row_spec(4, background = "#eff2b6") %>%
  footnote(symbol = c(footnote3, "Southern U.S. is limited to US fisheries south of the Canadian border.", footnote2, big.bar.footnote), threeparttable = T)




# table1form <- kable(t1, format = "latex", digits = c(0), format.args = list(big.mark =","), escape = T,
#                     col.names = c("Management unit", "Status", "ER Cap", "ER Model", "Southern US ER Model", "Cdn ER Model", "Escapement", "Recruitment (Ocean Age-3)"), label = "GUYUYUYUYUY",
#                     booktabs = T, linesep = "") %>%
#   kableExtra::column_spec(8:8, "2.5cm") %>%
#   kable_styling(latex_options = "striped") %>%
#   add_header_above(c(" ", "Pre-Season" = 7))




print(table1form)


```


\newpage 
\thispagestyle{empty}

**Table 2: Pre-season summary exploitation rates, escapements, and cohort abundances for naturally spawning Coho MUs in `r run.year`.**


```{r thirdtable, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

t3_per <- CreateTable3(pre.season.data) %>%
    filter(psc.fishery.name %notin% c("escapement", "cohort")) %>%
    mutate(`Interior Fraser without Big Bar` = (`Interior Fraser`*as.numeric(ifc.oa))/ifc.bb.returns) %>%
    mutate_if(is.numeric, ~percent(.,accuracy = 0.1, suffix = "\\%")) 

t3_cnt <-CreateTable3(pre.season.data)%>%
  filter(psc.fishery.name %in% c("escapement", "cohort")) %>%
  mutate(`Interior Fraser without Big Bar` = c(big.bar.esc, ifc.bb.returns)) %>%
  mutate_if(is.numeric, ~comma(.))


t3_cnt_GS <- select(t3_cnt, c("psc.fishery.name", starts_with("Georgia")))

t3_cnt_GS[1,2:ncol(t3_cnt_GS)] <- paste0(t3_cnt_GS[1,2:ncol(t3_cnt_GS)], footnote_marker_symbol(3))
t3_cnt_GS[2,2:ncol(t3_cnt_GS)] <- paste0(t3_cnt_GS[2,2:ncol(t3_cnt_GS)], footnote_marker_symbol(2))

t3_cnt_oth <- select(t3_cnt, -starts_with("Georgia")) %>%
  mutate(`Lower Fraser` = if_else(psc.fishery.name == "escapement",
                                  paste0(`Lower Fraser`, footnote_marker_symbol(1)," "),
                                  paste0(`Lower Fraser`, footnote_marker_symbol(2))))

t3_cnt <- left_join(t3_cnt_GS, t3_cnt_oth, "psc.fishery.name")


t3 <- bind_rows(t3_per, t3_cnt) %>%
  mutate(psc.fishery.name = str_replace(psc.fishery.name, "&", "\\\\&")) %>%
  rename(`Fishery Name` = "psc.fishery.name") %>%
    select(1, 4, 2, 3, 14, everything())


table3form <-  kable(t3, escape = F, booktabs= T, linesep = "", align = c('l', rep('c', nrow(t3)-1)), row.names = FALSE,  col.names = linebreak(c("Fishery name", "Georgia\nStrait", "Lower\nFraser","Interior\nFraser", paste0("Interior Fraser\nw/o Big Bar morts",  footnote_marker_symbol(4, "latex")), "Skagit", "Stillaguamish", "Snohomish", "Hood\nCanal", "US Strait\nJDF", "Quillayute", "Hoh", "Queets", "Grays\nHarbor"))) %>%
  kable_styling(latex_options = c("scale_down", "hold_position")) %>%
  column_spec(1, bold = T) %>%
  row_spec(c(13, 23, 25), background = "#e3e7fc") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(seq(2, nrow(t3),2)), background = "#d6d6d6") %>%
  column_spec(5,background = "#eef58c") %>%
  footnote(symbol = c("Modelled values of terminal run size occuring after lower Fraser in river fisheries", " Modelled values of terminal run size that are not directly estimated", "Modelled values that are not directly estimated", big.bar.footnote), threeparttable = T)


print(table3form)

```

